Owlifier: Creating OWL-DL Ontologies from Simple Spreadsheet-Based Knowledge Descriptions\tnoteref{t1}

### 2008-11-25 docs/pubs/ISEI6/main.tex

@@

>>>>

Notes: 
\begin{itemize}
\item we generally follow the guidelines in ontology creation of
  Rector et al. in \cite{rector04:_owl_pizzas}.
\item we also try to simplify certain aspects, e.g., disjoint classes
  and open-world reasoning, which can be confusing for non-experts
\item we try to use more meaningful terms, when applicable (e.g., instead of datatype property, attribute, etc.)
\item our goal is to not support all constructs in OWL-DL, but to
  provide the most commonly used ones for defining typical ontologies,
  but still allow experts to refine the ontology in ontology editing
  tools if necessary
\end{itemize}

@@

\section{\owlifier\ Properties and Reasoning}
\label{sec:properties}

Some desirable properties: 
\begin{itemize}
\item non-ambiguous (no block leads to ambiguous DL axioms)
\item ``reasonable'' (not everything has to be explicitly stated)
\item ???
\end{itemize}

\section{\owlifier\ Implementation}
\label{sec:implementation}

Flags: 
\begin{itemize}
\item delimeter characters 
\item perform classification
\item warnings
\item owlifier to owl and owl to owlifier
\item ??? 
\end{itemize}

\section{Conclusion}
\label{sec:conclusion}
